Evidence for a Color Parameter Unassociated With Dust Within the Type~Ia Supernovae of the Nearby Supernova Factory

### 2016-11-11 apj.tex
finish Jakob's comments

The Pearson correlation coefficients for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, $E_{\gamma^1}(B-V)$,  $A_{\delta I}$ are given in the matrix.
\begin{multline}
Cor(\Delta, EW_{Ca}, EW_{Si}, \lambda_{Si}, E_{\gamma^0}(B-V), E_{\gamma^1}(B-V),  A_{\delta I}) =\\
\begin{pmatrix}
\begin{array}{rrrrrrr}
1.00 & 0.01 & -0.06 & -0.05 & 0.11 & 0.01 & -0.03 \\
0.01 & 1.00 & 0.11 & -0.26 & -0.07 & -0.00 & 0.05 \\
-0.06 & 0.11 & 1.00 & -0.14 & -0.17 & -0.03 & -0.02 \\
-0.05 & -0.26 & -0.14 & 1.00 & 0.04 & 0.03 & 0.01 \\
0.11 & -0.07 & -0.17 & 0.04 & 1.00 & 0.06 & 0.03 \\
0.01 & -0.00 & -0.03 & 0.03 & 0.06 & 1.00 & -0.00 \\
-0.03 & 0.05 & -0.02 & 0.01 & 0.03 & -0.00 & 1.00
\end{array}
\end{pmatrix}.
\end{multline}
The intrinsic parameter $A_{\delta I}$ has correlations $<0.05$ with respect to all the other parameters, including those attributed
to extrinsic dust.

>>>>

The Pearson correlation coefficients for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, $E_{\gamma^1}(B-V)$,  $A_{\delta I}$ are given in the matrix.
\begin{multline}
Cor(\Delta, EW_{Ca}, EW_{Si}, \lambda_{Si}, E_{\gamma^0}(B-V), E_{\gamma^1}(B-V),  A_{\delta I}) =\\
\begin{pmatrix}
\begin{array}{rrrrrrr}
1.00 & 0.01 & -0.06 & -0.05 & 0.11 & 0.01 & -0.03 \\
0.01 & 1.00 & 0.11 & -0.26 & -0.07 & -0.00 & 0.05 \\
-0.06 & 0.11 & 1.00 & -0.14 & -0.17 & -0.03 & -0.02 \\
-0.05 & -0.26 & -0.14 & 1.00 & 0.04 & 0.03 & 0.01 \\
0.11 & -0.07 & -0.17 & 0.04 & 1.00 & 0.06 & 0.03 \\
0.01 & -0.00 & -0.03 & 0.03 & 0.06 & 1.00 & -0.00 \\
-0.03 & 0.05 & -0.02 & 0.01 & 0.03 & -0.00 & 1.00
\end{array}
\end{pmatrix}.
\end{multline}
The intrinsic parameter $A_{\delta I} =\delta_I D$ has correlations $<0.05$ with respect to all the other parameters, including those attributed
to extrinsic dust.
